\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage[margin=2.5cm]{geometry}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[nottoc,numbib]{tocbibind}

\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{\thepage}
\lhead{\thechapter . \leftmark}
\renewcommand{\chaptermark}[1]{ \markboth{#1}{} }

\linespread{1.3}

\DeclareMathOperator\arccosh{arccosh}
\DeclareMathOperator\sgn{sgn}

\begin{document}
	\input{title/title}
	%\include{statement/statement}
	\include{abstract/abstract}
	\include{aims/aims}
	\include{novelty/novelty}
	\include{publications/publications}
	\include{acknowledgements/acknowledgements}
	\tableofcontents
	%\listoffigures
	\include{introduction/introduction}
	\include{potential-step/potential-step}
	\include{potential-barrier/potential-barrier}
	\include{asymmetrical-barrier/asymmetrical-barrier}
	\include{experimental/experimental}
	\include{weyl-fermions/weyl-fermions}
	\include{wkb-potential-barrier/wkb-potential-barrier}
	\include{conclusion/conclusion}
	\include{appendix/appendix}
	\begin{thebibliography}{10}

\bibitem{b68}Das Adsorptionsverhalten sehr dünner Kohlenstoff-Folien\\
H. P. Boehm, A. Clauss, G. O. Fischer and U. Hofmann,
Das Adsorptionsverhalten sehr dünner Kohlenstoff-Folien. Z. anorg. allg. Chem., {\bf 316}: 119–127, (1962).

\bibitem{b64}Course of Theoretical Physics, Volume 5, Statistical Physics, Page 402\\
L. D. Landau and E. M. Lifshitz,
Pergamon Press LTD. (1960)

\bibitem{b69}Bemerkungen über Umwandlungstemperaturen\\
R. Peierls,
Helv. Phys. Acta {\bf 7}, 81 (1934).

\bibitem{b65}Electric Field Effect in Atomically Thin Carbon Films\\
K. S. Novoselov, A. K. Geim, S. V. Morozov, D. Jiang, Y. Zhang, S. V. Dubonos, I. V. Grigorieva and A. A. Firsov
Science {\bf 306}, pp. 666-669, (2004).

\bibitem{b70}Graphene: Status and Prospects\\
A. K. Geim,
Science {\bf 324}, 1530, (2009).

\bibitem{b66}The structure of suspended graphene sheets\\
J. C. Meyer, A. K. Geim, M. I. Katsnelson, K. S. Novoselov, T. J. Booth and S. Roth,
Nature {\bf 446}, (2007).

\bibitem{b67}Breakdown of continuum mechanics for nanometre-wavelength rippling of graphene\\
L. Tapaszt{\' o}, T. Dumitric{\u a}, S. J. Kim, P. Nemes-Incze, C. Hwang and L. P. Bir{\' o},
Nature {\bf 446}, (2007).

\bibitem{b5} The rise of graphene\\
A. K. Geim and K. S. Novoselov,
Nature Physics, Vol 6, (2007).

\bibitem{b46} Introduction to Graphene Electronics - A New Era of Digital Transistors and Devices\\
K. C. Yung, W. M. Wu, M. P. Pierpoint, F. V. Kusmartsev,
Cont. Phys. {\bf 54}, 233-251 (2013).

\bibitem{b62}Energetics of interplanar binding in graphite\\
M. C. Schabel and J. L. Martins,
Phys. Rev. B, {\bf 46}, No. 11, (1992).

\bibitem{b58}Measurement of the Elastic Properties and Intrinsic Strength of Monolayer Graphene\\
C. Lee, X. Wei, J. W. Kysar and J. Hone,
Science, {\bf 321}, 385, (2008).

\bibitem{b63}Young’s modulus of single-walled nanotubes\\
A. Krishnan, E. Dujardin, T. W. Ebbesen, P. N. Yianilos and M. M. J. Treacy,
Phys. Rev. B, {\bf 58}, No. 20, (1998).

\bibitem{b60}Thermal properties of graphene: Fundamentals and applications\\
E. Pop, V. Varshney and A. K. Roy,
MRS Bulletin, {\bf 37}, (2012).

\bibitem{b45}Ultrahigh electron mobility in suspended graphene\\
K. I. Bolotin, K. J. Sikes, Z. Jiang, M. Klima, G. Fudenberg, J. Hone, P. Kim and H.L. Stormer,
Solid State Commun., {\bf 146}, 351, (2008).

\bibitem{b61}Intrinsic and Extrinsic Performance Limits of Graphene Devices on SiO$_{2}$\\
J.H. Chen, C. Jang, S. Xiao, M. Ishigami and M. S. Fuhrer,
Nature Nanotech. {\bf 3}, 206 - 209, (2008).

\bibitem{b8} The Band Theory of Graphite\\
P. R. Wallace,
Physical Review, {\bf 71}, Number 9, (1947).

\bibitem{b1}	The electronic properties of graphene\\
A. H. Castro-Neto, F. Guinea, N. M. R. Peres, K. S. Novoselov, and A. K. Geim,
Rev. Mod. Phys. {\bf 81}, 109, (2009).

\bibitem{b55}Uniaxial strain on gapped graphene\\
M. Farjam and H. Rafii-Tabar,
Physica E, {\bf 42}, Issue 8, 2109-2114, (2010).

\bibitem{b44} \"{U}ber die Quantenmechanik der Elektronen in Kristallgittern.\\
F. Bloch,
Z. Physik, {\bf 52}, p.555, (1928).

\bibitem{b11} Klein tunneling in single and multiple barriers in graphene\\
J.M. Pereira Jr, F. M. Peeters, A. Chaves and G. A. Farias,
Semicond. Sci. Technol. {\bf 25}, 033002 (9pp), (2010).

\bibitem{b2} Confined states and direction-dependent transmission in graphene quantum wells\\
J. M. Pereira, V. Mlinar, F. M. Peeters and P. Vasilopoulos,
Phys. Rev. B {\bf 74}, 045424, (2006).

\bibitem{b4} Electron tunneling in single layer graphene with an energy gap\\
X. Xu-Guang, Z. Chao, Xu. Gong-Jie and C. Jun-Cheng,
Chin. Phys. B, {\bf 20}, No.2, 027201, (2011).

\bibitem{b47} A Stable "Flat" Form of Two-Dimensional Crystals: Could Graphene, Silicene, Germanene Be Minigap Semiconductors\\
A. O'Hare, F. V. Kusmartsev and K. I. Kugel,
Nano Lett., {\bf 12}, 1045, (2012).

\bibitem{b41} Semimetalic properties of a heterojunction\\
F. V. Kusmartsev and A. M. Tsvelik,
JETP lett., {\bf 42}, No. 5, 257-260, (1985).

\bibitem{b59}Uniaxial Strain on Graphene: Raman Spectroscopy Study and Band-Gap Opening\\
Z. H. Ni, T. Yu, Y. H. Lu, Y. Y. Wang, Y. P. Feng  and Z. X. Shen,
ACS Nano, {\bf 2} (11), 2301-2305, (2008).

\bibitem{b12} Chiral tunneling and the Klein paradox in graphene\\
M. I. Katsnelson, K.S. Novoselov and A. K. Geim,
Nature Physics, {\bf 2}, (2006).

\bibitem{b3}	Voltage-driven quantum oscillations in graphene\\
V. A. Yampol'skii, S. Savel'ev and F. Nori,
New J. Phys. {\bf 10}, 053024, (2008).

\bibitem{b39}Zur Theorie des Diamagnetismus von Leitungselektronen\\
R. Peierls
Zeitschrift für Physik, {\bf 80}, Issue 11-12, (1933).

\bibitem{b33} Course of Theoretical Physics, Volume 3, Quantum Mechanics\\
L. D. Landau and E. M. Lifshitz,
Pergamon Press LTD., (1960).

\bibitem{b37} Electronic properties of graphene in a strong magnetic field\\
M. O. Goerbig,
Rev. Mod. Phys. {\bf 83}, 1193, (2011).

\bibitem{b53}Magnetisation oscillations, boundary conditions and the Hofstadter butterfly in graphene flakes\\
Y. Liu, M. Brada, E. J. Mele and F. V. Kusmartsev,
Ann. Phys. (Berlin), {\bf 526}, No. 9–10, 449–460, (2014).

\bibitem{b6} Generalized many-channel conductance formula with application to small rings\\
M. buttiker, Y. Imry, R. Landauer and S. Pinhas,
Physical Review B, {\bf 31}, Number 10, (1985).

\bibitem{b7} Relation beteen conductivity and transmission matrix\\
D. S. Fisher and P. A. Lee,
Physical Review B, {\bf 23}, Number 12, (1981).

\bibitem{b9} Electronic Transport in Mesoscopic Systems\\ 
S. Datta,
Cambridge University Press, (1995).

\bibitem{b10} Transition from metalic to tunneling regeimes in superconducting microstructures: Excess current, charge imbalance, and supercurrent conversion\\
G. E. Blonder, M. Tinkham and T. M. Klapwijk,
Phys. Rev. B, {\bf 25}, No. 7, (1982).

\bibitem{b14} Fabry-P\'{e}rot resonances in graphene microstructures: Influence in magnetic field\\
M. R. Masir, P. Vasilopoulos and F. M. Peeters,
Phys. Rev. B, {\bf 82}, 115417, (2010).

\bibitem{b15} Tunneling of Dirac electrons through spactial regions of finite mass\\
J. V. Gomes and N. M. R. Peres,
J. Phys.:Condens. Matter, {\bf 20}, 324221, (2008).

\bibitem{b13} Electronic transmission through p-n and n-p-n junctions of graphene\\
M.R. Setare and D. Jahani,
J. Phys.: Condens. Matter, {\bf 22}, 245503, (2010).

\bibitem{b16} Design of electron wave filters in monolayer graphene by tunable transmission gap\\
X. Chen and J. Tao,
Appl. Phys. Lett., {\bf 94}, 262102, (2009).

\bibitem{b40}Chiral tunneling in single-layer and bilayer graphene\\
T. Tudorovskiy, K. J. A. Reijnders and M. I. Katsnelson
Phys. Scr., {\bf T146}, 014010, (17pp), (2012).

\bibitem{b18} Wave Propagation: From Electrons to Photonic Crystals and Left-Handed Materials\\
P. Markos and C. M. Soukoulis,
Princeton University Press, (2008).

\bibitem{b48} Common-path interference and oscillatory Zener tunneling in bilayer graphene p-n junctions\\
R. Nandkishore and L. Levitov,
PNAS, {\bf 108}, No. 34, 14021-14025, (2011).

\bibitem{b57}Transport in carbon nanotube p-i-n diodes\\
K. Bosnick, N. Gabor and P. McEuen,
Appl. Phys. Lett., {\bf 89}, 163121, (2006).

\bibitem{b17} Klein tunneling of massive Dirac fermions in single-layer graphene\\
M.R. Setare and D. Jahani,
\newblock Physica B, {\bf 405}, 1433-1436, (2010)

\bibitem{b49} Die Reflexion von Elektronen an einem Potentialsprung nach der relativistischen Dynamik von Dirac\\
O.Klein,
Z. Physik, {\bf 53}, 157, (1929).

\bibitem{b38} Klein Backscattering and Fabry-Pérot Interference in Graphene Heterojunctions\\
A.i V. Shytov, M. S. Rudner and L. S. Levitov,
Phys. Rev. Lett., {\bf 101}, 156804, (2008).

\bibitem{b32} Course of Theoretical Physics, Volume 9, Statistical Physics Part 2\\
L. D. Landau and E. M. Lifshitz,
Pergamon Press LTD., (1960).

\bibitem{b52}Physical properties of Zener tunnelling nano-devices in graphene\\
R. D. Y. Hills and F. V. Kusmartsev,
Ann. Phys. (Berlin), {\bf 526}, No. 9–10, 437–448, (2014).

\bibitem{b42} A Theory of the Electrical Breakdown of Solid Dielectrics\\
C. Zener,
Proc. R. Soc. Lond. A., {\bf 145}, 523-529, (1934).

\bibitem{b43} ZENER TUNNELING IN SEMICONDUCTORS\\
E. O. Kane,
J. Phys. Chem. Solids., {\bf 12}, pp 181-188, (1959).

\bibitem{b54}Current-voltage characteristics of graphene devices: Interplay between Zener-Klein tunneling and defects\\
N. Vandecasteele, A. Barreiro, M. Lazzeri, A. Bachtold and F. Mauri,
Phys. Rev. B, {\bf 82}, 045416, (2010).

\bibitem{b19} Exeptional ballistic transport in epitaxial graphene nanoribbons\\
J. Baringhaus, M. Ruan, F.Edler, A.Tejeda, M. Sicot, A. Ibrahimi, A. Li, Z. Jiang, E. Conrad, C. Berger, C. Tegenkamp and W. A. de Heer
Nature, {\bf 506}, 349, (2014).

\bibitem{b20} Quantum Dot Behaviour in Graphene Nanoconstrictions\\
K. Todd, H. Chou, S. Amasha and D. Goldhaber-Gordon,
Nano Letters, {\bf 9}, No. 1 416-421, (2009).

\bibitem{b21} Electron Transport in Disordered Graphene Nanoribbons\\
M. Y. Han, J. C. Brant and P. Kim,
Phys. Rev. Lett., {\bf 104}, 056801, (2010).

\bibitem{b22} Electrical observation of subband formation in graphene nanoribbons\\
Y. Lin, V. Perebeinos, Z. Chen and P. Avouris,
Phys. Rev. B, {\bf 78}, 161409(R), (2008).

\bibitem{b56}Electronic transport in graphene-based heterostructures\\
J. Y. Tan, A. Avsar, J. Balakrishnan, G. K. W. Koon, T. Taychatanapat, E. C. T. O'Farrell, K. Watanabe, T. Taniguchi, G. Eda, A. H. Castro Neto and B. Özyilmaz,
Appl. Phys. Lett., {\bf 104}, 183504, (2014).

\bibitem{b71}The Birth of Topological Insulators\\
J. E. Moore, 
Nature, {\bf164}, pp. 194-198, (2010).

\bibitem{b23} Large magnetiresistance in non-magnetic silver chalcogenides\\
R. Xu, A. Husmann, T. F. Rosenbaum, M.-L Saboungi, J. E. Enderby and P. B. Littlewood,
Nature, {\bf 390}, (1997).

\bibitem{b24} Energy Gap in $\beta$-Ag$_{2}$Se\\
R. Dalven and R. Gill,
Physical Review, {\bf 159}, No. 3, (1967).

\bibitem{b25} Quantum linear magnetoresistance; solution of an old mystery\\
A. A. Abrikosov,
J. Phys. A: Math. Gen., {\bf 36}, 9119-9131, (2003).

\bibitem{b26} BAND STRUCTURE OF GRAY TIN\\
S. Groves and W. Paul,
Phys. Rev. Lett., {\bf 11}, No. 5, (1963).

\bibitem{b27} Mercury telluride - a zero-gap semiconductor\\
N. N. Berchenko and M. V. Pashkovskii,
Sov. Phys. Usp., {\bf 19}, No. 6, (1976).

\bibitem{b28} Observation of three-dimensional massless Kane fermions in a zinc-blende crystal\\
M. Orlita, D. M. Basko, M. S. Zholudev, F. Teppe, W. Knap, V. I. Gavrilenko, N. N. Mikhailov, S. A. Dvoretskii, P. Neugebauer, C. Faugeras, A-L. Barra, G. Martinez and M. Potemski,
Nature Physics, {\bf 10}, (2014).

\bibitem{b29} Discovery of a Three-Dimensional Topological Dirac Semimetal Na$_{3}$Bi
Z. K. Liu, B. Zhou, Y. Zhang, Z. J. Wang, H. M. Weng, D. Prabhakaran, S. K. Mo, Z. X. Shen, Z. Fang, X. Dai, Z. Hussain and Y. L. Chen,
Science, {\bf 343}, 864, (2014).

\bibitem{b34} A stable three-dimensional topological Dirac semimetal Cd$_{3}$As$_{2}$\\
Z. K. Liu1, J. Jiang, B. Zhou, Z. J.Wang, Y. Zhang, H. M.Weng, D. Prabhakaran, S. K. Mo, H. Peng, P. Dudin, T. Kim, M. Hoesch, Z. Fang, X. Dai, Z. X. Shen, D. L. Feng, Z. Hussain and Y. L. Chen
Nature Materials, {\bf 3}, (2014)

\bibitem{b35}Observation of a three-dimensional topological Dirac semimetal phase in high-mobility Cd$_{3}$As$_{2}$\\
M. Neupane, S. Xu, R. Sankar, N. Alidoust, G. Bian, C. Liu, I. Belopolski, T. Chang, H. Jeng, H. Lin, A. Bansil, F. Chou and M. Z. Hasan,
Nat. Commun., 5:3786, doi: 10.1038/ncomms4786, (2014).

\bibitem{b36}Three-dimensional Dirac semimetal and quantum transport in Cd$_{3}$As$_{2}$\\
Z. Wang, H. Weng, Q. Wu, X. Dai, and Z. Fang,
Phys. Rev. B, {\bf 88}, 125427, (2013).

\bibitem{b50} Topological semimetal and Fermi-arc surface states in the electronic structure of pyrochlore iridates\\
X. Wan, A. M. Turner, A. Vishwanath and S. Y. Savrasov,
Phys. Rev. B, {\bf 83}, 205101, (2011).

\bibitem{b51} Dirac Semimetal in Three Dimensions\\
S. M. Young, S. Zaheer, J. C. Y. Teo, C. L. Kane, E. J. Mele and A. M. Rappe,
Phys. Rev. Lett., {\bf 108}, 140405, (2012).

\bibitem{b30} Spectrum of localised states in graphene quantum dots and wires\\
V. V. Zalipaev, D. N. Maksimov, C. M. Linton and F. V. Kusmartsev,
Phys. Lett. A, {\bf 337}, 216-221, (2013).

\bibitem{b72}New Progress on Graphene Research: Chapter 2\\
V. V. Zalipaev, D. M. Forrester, C. M. Linton and F. V. Kusmartsev,
InTech, (2013).

\bibitem{b31} Semi-Classical Approximation in Quantum Mechanics\\
V. P. Maslov and M.V. Fedoriuk,
Springer, (2001).

%\bibitem{b45} ON THE PART OF THE MOTION OF THE LUNAR PERIGEE WHICH IS A FUNCTION OF THE MEAN MOMTIONS OF THE SUN AND MOON\\
%G. W. Hill,
%Acta Math., {\bf 8}, p.27, (1886).

%%%%% 72 references at this point %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{thebibliography}
\end{document}